A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Prohibtion is 0
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1014 43ef1190-90fd-4dd7-a769-d0121f02b80e

Of the 2965 resources, 405 returned valid headers, but 114 did so to
prohibit caching of the response, and 3 contained conflicting
headers, i.e. set an freshness lifetime, but also prohibited
caching. In most cases, \httph{Cache-Control} and \httph{Expires} both
occurred, but the former is more common than the latter in the cases
where only one of them occur.  Additionally, 269 resources had a
\httph{Cache-Control} header to control other aspects of caching than
lifetime, i.e. to say that only private caches may use the response,
that the cache must be revalidated, or to prohibit caching.

% todo: kill this?
Common practice when prohibiting caching is to set the \httph{Expires}
header to a date far back in time, which has also been done in large
parts of the present dataset. For the following, we have set any
non-positive lifetime to 0, as that is semantically equivalent.

>>>>

Of the 2965 resources, 405 returned valid headers, but 114 did so to
prohibit caching of the response, and 3 contained conflicting
headers, i.e. set an freshness lifetime, but also prohibited
caching. In most cases, \httph{Cache-Control} and \httph{Expires} both
occurred, but the former is more common than the latter in the cases
where only one of them occur.  Additionally, 269 resources had a
\httph{Cache-Control} header to control other aspects of caching than
lifetime, i.e. to say that only private caches may use the response,
that the cache must be revalidated, or to prohibit caching. Note that the
freshness lifetime is 0 whenever caching is prohibited.
